---
title: "Erigenia_Fstats_GenDiv"
author: "CLM"
date: "8/4/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
library(hierfstat)
library(gaston)
library(vcfR)
library(reshape2)
library(pegas)
library(cowplot)
```


```{r}
setwd("~/Documents/RStudio/Erigenia/Erigenia_Analyses/vcf_tools")
```

```{r read in vcf with vcfR}
vcf<-read.vcfR("erigeniaC_noMD_filtered.recode_14350_118.vcf")
```


#Getting data into hierfstat
```{r vcf to genind}
new_Erigenia_genind<- vcfR2genind(vcf)
```
```{r assigning pops}
pop(new_Erigenia_genind) <- as.factor(c("PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek"))
popNames(new_Erigenia_genind)
```
```{r genind to hierfstat}
new_Erigenia_hfstat<-genind2hierfstat(new_Erigenia_genind,pop=NULL)
```


#Basic stats with dartR
```{r}
gl.basic.stats(new_Erigenia_gl)
```

$overall
    Ho     Hs     Ht    Dst    Htp   Dstp    Fst   Fstp    Fis   Dest 
0.0553 0.1530 0.3171 0.1642 0.3406 0.1876 0.5176 0.5509 0.6385 0.2215 

can we do per pop?


#Basic stats with hierfstat
basicstat is a hierfstat function to tell you Fis etc
edit to work with 
https://cran.r-project.org/web/packages/hierfstat/vignettes/import.html

```{r}
basicstat <- basic.stats(new_Erigenia_hfstat, diploid=TRUE, digits=3)
```
```{r}
save(basicstat, file="basicstat.RData")
```

```{r}
names(basicstat)
```
```{r}
overall_basic_stats <- as.data.frame(basicstat$overall)
overall_basic_stats
basicstat$pop
```
     basicstat$overall
Ho               0.055
Hs               0.153
Ht               0.317
Dst              0.164
Htp              0.341
Dstp             0.188
Fst              0.518
Fstp             0.551
Fis              0.639
Dest             0.222


These are very similar to values above from dartR

get bootstrap confidence values for Fis
```{r}
boot<- boot.ppfis(new_Erigenia_hfstat, nboot=1000)
boot5<-boot.ppfis(new_Erigenia_hfstat, nboot=1000, quant=0.5)
```


```{r}
boot
boot5
```

```{r}
new_Erigenia_hfstat$pop
pop_order<- c("PeachBottom", "YorkFurnace", "SafeHarbor", "RacoonCreek", "CedarCreek", "BraddockTrail", "RyersonStation", "SlipperyRockCreek")
colnames(basicstat$Ho) <- pop_order
```
```{r}
Ho <- colMeans(basicstat$Ho,na.rm=T)
He <- colMeans(basicstat$Hs,na.rm=T)
Fis <- boot5$fis.ci$ll
new_popgen_stats <- cbind(Ho,He,Fis,boot$fis.ci)
new_popgen_stats
```
                        Ho         He    Fis     ll     hl
PeachBottom       0.03150687 0.12559844 0.7490 0.7403 0.7576
YorkFurnace       0.03737046 0.10250698 0.6351 0.6231 0.6469
SafeHarbor        0.02749131 0.06226778 0.5578 0.5379 0.5757
RacoonCreek       0.02864231 0.10787123 0.7345 0.7234 0.7461
CedarCreek        0.05319950 0.14503398 0.6331 0.6235 0.6427
BraddockTrail     0.09522822 0.21888139 0.5649 0.5581 0.5718
RyersonStation    0.07985895 0.22134690 0.6393 0.6322 0.6462
SlipperyRockCreek 0.08887310 0.23183168 0.6169 0.6094 0.6234

```{r}
popgen_stats_noMD.csv <-write.table(new_popgen_stats, sep=",", dec=".", row.names=TRUE, col.names=TRUE)

save(new_popgen_stats, file="new_popgen_stats")
```

#Fst
This is with hierfstat but dartR suggests a package called stampp if you want to double check


This takes a long time (~30 minutes)
```{r calculate fst}
fst.mat<-genet.dist(new_Erigenia_hfstat, method = "WC84")
```
```{r}
gindF.fst.mat.tri <- as.matrix(fst.mat)
colnames(gindF.fst.mat.tri)<- pop_order
rownames(gindF.fst.mat.tri)<- pop_order
write.table(gindF.fst.mat.tri, file="ErigeniaFstWC84.pwfst", row.names=T,col.names=T)
```


```{r}
melted <- melt(gindF.fst.mat.tri, na.rm = TRUE)
```

   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2929  0.4799  0.4436  0.6120  0.7920

```{r}
summary(melted$value)
```
  Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
 0.0000  0.2929  0.4799  0.4436  0.6120  0.7920


FIGURE FOR PUB
plotting using ggplot2

```{r figure for fst}
combined <- ggplot(data = melted, aes(Var2, Var1, fill = value))+ geom_tile(color = "white")+ 
  scale_fill_gradient(low = "white", high = "red", name="FST")  +
  ggtitle(expression(atop("Pairwise FST, WC (1984), Combined", atop(italic("N = 118"), ""))))+
  labs( x = "Sampling Site", y = "Sampling Site") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1),axis.text.y = element_text(size = 13)) + 
  coord_fixed()
combined
```


can also do regional
check Fst_per_Silliman if you want to 

#Bartlett Test


```{r}
ErigeniaHet <- summary(new_Erigenia_genind)
ErigeniaHet
```

```{r saving het}
save(ErigeniaHet,file="ErigeniaHet.Rdata")
```

```{r}
names(ErigeniaHet)
```


supplemental figures
```{r}
#tiff(filename="Erigenia_Hob_plot.tiff", width = 4, height = 4, units = 'in', res = 300)
plot(ErigeniaHet$Hobs, xlab="Locus number", ylab="Observed heterozygosity", main="Observed heterozygosity per locus")
#dev.off()
```

```{r}
#tiff(filename="Erigenia_Ho_He_plot.tiff", width = 4, height = 4, units = 'in', res = 300)
plot(ErigeniaHet$Hobs, ErigeniaHet$Hexp, xlab="Observed heterozygosity", ylab="Expected heterozygosity", main="He as a function of Ho, per locus")
#dev.off()
```

#Barlett Test

```{r}
bartlett.test(list(ErigeniaHet$Hexp, ErigeniaHet$Hobs))
```
Bartlett test of homogeneity of variances

data:  list(ErigeniaHet$Hexp, ErigeniaHet$Hobs)
Bartlett's K-squared = 7103.1, df = 1, p-value < 2.2e-16
wow: across PA, Ho is very low, statistically significantly so.

Now, separate pops and repeat Bartlett for each.
Use seppop in adegenet to split the genind by population. use pop=NULL to let it use the pop slot in the big genind, makes a list.
```{r}
temp_seppop <- seppop(new_Erigenia_genind)
```
make individual geninds from the list
```{r}
PB <- temp_seppop$PeachBottom
BTP <- temp_seppop$BraddockTrail
CCP <- temp_seppop$CedarCreek
RCSPWR <- temp_seppop$RaccoonCreek
RSSP <- temp_seppop$RyersonStation
SH <- temp_seppop$SafeHarbor
SRCNA <- temp_seppop$SlipperyRockCreek
YF <- temp_seppop$YorkFurnace
```

each pop can now be called! do bartletts for each.
```{r}
PBHet <- summary(PB)
bartlett.test(list(PBHet$Hexp, PBHet$Hobs))
```
Bartlett's K-squared = 8189.6, df = 1, p-value < 2.2e-16
woo!

```{r}
BTPHet <- summary(BTP)
bartlett.test(list(BTPHet$Hexp, BTPHet$Hobs))
```
Bartlett's K-squared = 2720.5, df = 1, p-value < 2.2e-16

```{r}
CCPHet <- summary(CCP)
bartlett.test(list(CCPHet$Hexp, CCPHet$Hobs))
```
Bartlett's K-squared = 4495.7, df = 1, p-value < 2.2e-16

```{r}
RCSPWRHet <- summary(RCSPWR)
bartlett.test(list(RCSPWRHet$Hexp, RCSPWRHet$Hobs))
```
Bartlett's K-squared = 6815.9, df = 1, p-value < 2.2e-16

```{r}
RSSPHet <- summary(RSSP)
bartlett.test(list(RSSPHet$Hexp, RSSPHet$Hobs))
```
Bartlett's K-squared = 3416.9, df = 1, p-value < 2.2e-16

```{r}
SHHet <- summary(SH)
bartlett.test(list(SHHet$Hexp, SHHet$Hobs))
```
Bartlett's K-squared = 3076.3, df = 1, p-value < 2.2e-16

```{r}
SRCNAHet<- summary(SRCNA)
bartlett.test(list(SRCNAHet$Hexp, SHHet$Hobs))
```
Bartlett's K-squared = 7087.1, df = 1, p-value < 2.2e-16

```{r}
YFHet <- summary(YF)
bartlett.test(list(YFHet$Hexp, SHHet$Hobs))
```
Bartlett's K-squared = 4109.2, df = 1, p-value < 2.2e-16
