---
title: "Erigenia_DAPC"
author: "AJM & CLM"
date: "5/22/2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

filter new vcf w/o MD from ipyrad:
```{bash}
(base) biol327-mac:erigeniaC_noMD_outfiles PostDoc$ vcftools --vcf erigeniaC_noMD.vcf --recode --recode-INFO-all --min-alleles 2 --max-alleles 2 --max-missing 0.75 --out filtered
```
VCFtools - 0.1.16
(C) Adam Auton and Anthony Marcketta 2009

Parameters as interpreted:
	--vcf erigeniaC_noMD.vcf
	--recode-INFO-all
	--max-alleles 2
	--min-alleles 2
	--max-missing 0.75
	--out filtered
	--recode

After filtering, kept 120 out of 120 Individuals
Outputting VCF file...
After filtering, kept 22525 out of a possible 436075 Sites
Run Time = 20.00 seconds

```{r}
library("adegenet")
if (!require("devtools")) install.packages("devtools")
devtools::install_github("tidyverse/dplyr", force=TRUE)
library("dplyr")
library("readr")
library("hierfstat")
```


```{r install package radiator}
#this gave us some issues
if (!require("devtools")) install.packages("devtools")
devtools::install_github("thierrygosselin/radiator", force=TRUE)
library("radiator")
```
```{r}
library("radiator")
```
```{r making sure the data is recognized}
radiator::detect_genomic_format(data="erigeniaC.noMD.filtered.recode.vcf")
```
This is how you should read in a vcf (not with vcfR)
```{r reading in vcf}
NewErigeniaCnoMD.vcf <- read_vcf("erigeniaC.noMD.filtered.recode.vcf")
```

convert vcf file to a genind object and a hierfstat object. Keeps markers common in all populations. hierfstat file made = something like radiator_data_20190508@1444.dat
genind also made with a logical name.

-Eventually we had to remove @ and changed to a so R would run code. If redoing these analyses try changing @ to a.


```{r read in strata file}
setwd("~/github/Erigenia-Analyses")
Erigenia.strata_noMD<-read.table("Erigenia.strata_noMD",sep="\t",header=TRUE)
```
```{r converting with radiator}
new.rad.filt <- radiator::genomic_converter("/Volumes/Thunderbolt/Users/PostDoc/Github/Erigenia-Analyses/erigeniaC.noMD.filtered.recode.vcf",
                       strata=Erigenia.strata_noMD,
                       output = c("genlight","hierfstat"),
                       parallel.core = 1, verbose=TRUE)
```

import genlight and radiator files from radiator output
```{r }
new_radiator_genlight_noMD <- read_rds("/Volumes/Thunderbolt/Users/PostDoc/Github/Erigenia-Analyses/296_radiator_genomic_converter_20190522a1616/radiator_genlight_20190522a1618.RData")
```
```{r}
save(new_radiator_genlight_noMD, file="new_radiator_genlight_noMD.RData")
```

```{r}
new_radiator_hf_noMD <- read.fstat("/Volumes/Thunderbolt/Users/PostDoc/Github/Erigenia-Analyses/296_radiator_genomic_converter_20190522a1616/radiator_data_20190522a1616.dat", na.s = c("0","00","000","0000","00000","000000","NA"))
```

assign pops to pop slot in genlight
```{r}
pop<-Erigenia.strata_noMD$LOCATION
```


#Doing DAPC

Helpful links: 
https://grunwaldlab.github.io/Population_Genetics_in_R/DAPC.html
http://adegenet.r-forge.r-project.org/files/tutorial-dapc.pdf
 -Code to explore DAPC objects and assignments
```{r}
grp<-find.clusters(new_radiator_genlight_noMD)
```
```{r}
grp
```
```{r}
dapc1<- dapc(new_radiator_genlight_noMD, grp$grp)
```
```{r}
#dapc1
dapc$assign
```
```{r}
dapc1$posterior
```
```{r}
Erigenia.dapc$posterior
```
```{r}
loadingplot(Erigenia.dapc$var.contr)
```
```{r}
summary(Erigenia.dapc)
```

```{r}
assignplot(Erigenia.dapc)
```

make a dapc in adegenet, 3 pca's, 2 axes (may take some time)
```{r}
Erigenia.dapc <- dapc(new_radiator_genlight_noMD, n.pca=3, n.da=2)
```
-------------------





MAKING FIGURES
```{r save fig}
myCol <- c("brown","purple","green","orange","red","blue","black","yellow")
#pdf("DAPC.pdf", width = 4, height = 4)
scatter(Erigenia.dapc, posi.da="bottomright", bg="white",
pch=17:22, cstar=0, col=myCol, scree.pca=TRUE,
posi.pca="bottomleft")
#dev.off()
```

Basic=scatter.dapc(Erigenia.dapc); Can add more arguments  to above code and change other features

```{r}
scatter(Erigenia.dapc, scree.da=FALSE, bg="white", pch=20, cell=0, cstar=0, col=colors, solid=.4,
cex=3,clab=0, leg=TRUE, txt.leg=paste("Cluster",1:8))
```


------------- Investigating number of PCs with alpha values etc
http://adegenet.r-forge.r-project.org/files/tutorial-dapc.pdf pg 37

```{r}
x<-(radiator_hf_a_noMD)
```
swapped new_radiator_genlight_noMD out

```{r}
mat<- as.matrix(x)
```
You need to remove na from matrix not genlight (S4) b/c na.replace in adegenet is gone
```{r}
mat<- na.replace(mat, mean, na.rm=TRUE) 
```
OR
```{r}
mat <- as.matrix(x, missing="mean")
```


```{r}
grp2<- pop(x)
```
```{r}
grp2
```


```{r}
xval <- xvalDapc(mat, grp2, n.pca.max = 120, n.da=NULL, training.set = 0.9,
result = "groupMean", center = TRUE, scale = FALSE,
n.pca = NULL, n.rep = 30, xval.plot = TRUE)
```
current error: Error in if (nf > rank) nf <- rank : missing value where TRUE/FALSE needed

issue with duplicate row names... maybe because I'm using a genlight not genind... I could use our old genind since it may contain MD but that shouldn't change PCs much 

try with not matirx
```{r}
xval<-xvalDapc(x2, grp2, n.pca.max = 300, n.da = NULL, training.set = 0.9, result = c("groupMean", "overall"), center = TRUE, scale = FALSE, n.pca=NULL, n.rep = 30, xval.plot = TRUE)

```
```{r}
x2<- as.data.frame(radiator_hf_a_noMD, missing="mean")
```
```{r}
x2 %>% tidyr::fill(everything(x2))
```



```{r read in genind}
radiator_genind_a <- read_rds("/Volumes/Thunderbolt/Users/PostDoc/Github/Erigenia-Analyses/a118_radiator_genomic_converter_20190508a1444/radiator_genind_20190508@1445.RData")
```



```{r}
adegenetServer(what = "DAPC")
```
new_radiator_genlight_noMD.RData

-----
# redoing dapc with alpha score consideration
```{r}
Erigenia.dapc2 <- dapc(new_radiator_genlight_noMD, n.pca=10, n.da=10)

```
```{r}
temp <- a.score(Erigenia.dapc2)
names(temp)
temp.<- optim.a.score(Erigenia.dapc2)
```
```{r}
temp$pop.score
temp$mean
```

```{r}
dapc3 <- dapc(new_radiator_genlight_noMD, n.da=100, n.pca=20)
temp2 <- optim.a.score(dapc3)
```
```{r}
dapc3 <- dapc(new_radiator_genlight_noMD, n.da=2, n.pca=15)
temp3 <- optim.a.score(dapc3)
```


```{r}
Erigenia.dapc_newPCs <- dapc(new_radiator_genlight_noMD, n.pca=5, n.da=2)

```
```{r}
Erigenia.dapc_newPCs$posterior
```

```{r}
loadingplot(Erigenia.dapc_newPCs$var.contr)
```
```{r}
summary(Erigenia.dapc_newPCs)
```

```{r}
scatter(Erigenia.dapc_newPCs, scree.da=FALSE, bg="white", pch=20, cell=0, cstar=0, col=colors, solid=.4,
cex=3,clab=0, leg=TRUE, txt.leg=paste("Cluster",1:8))
```

```{r save fig}
myCol <- c("burlywood4","darkviolet","green","orange","red","dodgerblue3","black","gold2")
pdf("DAPC.pdf", width = 6, height = 4)
scatter(Erigenia.dapc_newPCs, posi.da="bottomright", bg="white",
pch=17:22, cstar=0, col=myCol, scree.pca=TRUE,
posi.pca="topright")
dev.off()
```


```{r}
assignplot(Erigenia.dapc_newPCs)
```




#No luck with this... come back to? 
#STRUCTURE-like plot
```{r DAPC structure plot}
compoplot(Erigenia.dapc_newPCs,col = myCol, posi = 'bottom')
```
##ggplot

```{r}
dapc.results <- as.data.frame(Erigenia.dapc$posterior)
dapc.results$pop <- pop(new_radiator_genlight_noMD)
dapc.results$indNames <- row.names(dapc.results)
#dapc.results$Region <-Erigenia.strata_noMD$REGION
#region optional
```

```{r}
dapc.results <- melt(dapc.results)
colnames(dapc.results) <- c("Original_Pop","Sample","Assigned_Pop","Posterior_membership_probability")
```

```{r}
colors <- c("tomato", "black", "peachpuff4", "cadetblue1", "yellowgreen", "darkturquoise", 
            "orange", "purple")
BmyCol <- c("brown","purple","green","orange","red","blue","black","yellow")
```

```{r works}
p <- ggplot(dapc.results, aes(x=Sample, y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity')
p <- p + scale_fill_manual(values = colors)
p <- p + facet_grid(~Original_Pop, scales = "free")
p <- p + ylab("Posterior membership probability")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
p <- p + theme(axis.text.y = element_text(angle = 90, hjust = 1, size = 8))
p
```

```{r doesnt work}
p <- ggplot(dapc.results, aes(x=indNames, y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity')
p <- p + scale_fill_manual(values = colors)
p <- p + facet_grid(~pop, scales = "free")
p <- p + ylab("Posterior membership probability")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
p <- p + theme(axis.text.y = element_text(angle = 90, hjust = 1, size = 8))
p
```
```{r also doesn't work}
p <- ggplot(dapc.results, aes(x=Sample, y=Posterior_membership_probability, fill=Assigned_Pop))
p <- p + geom_bar(stat='identity')
p <- p + scale_fill_manual(values = colors)
p <- p + facet_grid(~Region, scales = "free")
p <- p + ylab("Posterior membership probability")
p <- p + theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
p <- p + theme(axis.text.y = element_text(angle = 90, hjust = 1, size = 8))
p
```
This isn't working like we thought it was, it's mixing up pops





#finding clusters if we want.. 
```{r DAPC clusters}
#n.iter for number of interations, can also set seed
#erigenia.clusts <- find.clusters(s_vib_gen, n.iter=100, max.n.clust=8)
```
