---
title: "Erigenia_IBD_amova"
author: "CLM"
date: "8/3/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

BELOW IS CODE FROM BAPTISIA ANALYSES WITH DARTR- edit to work for Erigenia
 
#Getting set up
```{r library}
library(adegenet)
library(pegas)
library(vcfR)
library(dartR)
library(poppr)
```

```{r}
setwd("~/Documents/RStudio/Erigenia/Erigenia_Analyses/vcf_tools")
```

```{r read in vcf with vcfR}
vcf<-read.vcfR("erigeniaC_noMD_filtered.recode_14350_118.vcf")
```


```{r convert}
new_Erigenia_gl <- vcfR2genlight(vcf)
```
```{r assigning pops}
pop(new_Erigenia_gl) <- as.factor(c("PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","PeachBottom","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","YorkFurnace","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","SafeHarbor","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","RaccoonCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","CedarCreek","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","BraddockTrail","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","RyersonStation","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek","SlipperyRockCreek"))
popNames(new_Erigenia_gl)
```

#Mantel Test 

```{r}
coords <- read.csv ("coords.csv", header=TRUE) #for each pop
#coords_all<-read.csv("coords_all.csv", header=TRUE) #for each individual
```

```{r alternative to assigning coords_all to the gl}
Dgen <- gl.dist.pop(new_Erigenia_gl, method="euclidean")
Dgeo <- dist(coords)
```
```{r}
Dgen
```

```{r not running this for Erigenia}
new_Erigenia_gl@other$latlong<-coords_all
new_Erigenia_gl@other$latlong
new_Erigenia_gl@pop
```

```{r didn't run}
Erigenia_ibd<- gl.ibd(gl = new_Erigenia_gl, Dgen = NULL, Dgeo = NULL, projected = TRUE,
  permutations = 999, plot = TRUE)
```


```{r dartR }
Erigenia_ibd_<- gl.ibd(gl = NULL, Dgen = Dgen, Dgeo = Dgeo, projected = TRUE,
  permutations = 999, plot = TRUE)
```
Erigenia_ibd_<- gl.ibd(gl = NULL, Dgen = Dgen, Dgeo = Dgeo, projected = TRUE,
+   permutations = 999, plot = TRUE)
Analysis performed on provided genetic and Euclidean distance matrices.
Mantel statistic based on Pearson's product-moment correlation 

Call:
mantel(xdis = Dgen, ydis = Dgeo, permutations = 999, na.rm = TRUE) 

Mantel statistic r: 0.944 
      Significance: 0.01 

Upper quantiles of permutations (null model):
  90%   95% 97.5%   99% 
0.171 0.229 0.267 0.934 
Permutation: free
Number of permutations: 999



```{r ade package}
Erigenia_ibd_2<- mantel.randtest(Dgen, Dgeo)
```


```{r}
Erigenia_ibd_2
plot(Erigenia_ibd_2)
```
Monte-Carlo test
Call: mantel.randtest(m1 = Dgen, m2 = Dgeo)

Observation: 0.944004 

Based on 999 replicates
Simulated p-value: 0.019 
Alternative hypothesis: greater 

    Std.Obs Expectation    Variance 
4.532095254 0.001750734 0.043225223




#AMOVA
##dartR
https://grunwaldlab.github.io/Population_Genetics_in_R/AMOVA.html
https://grunwaldlab.github.io/poppr/reference/poppr.amova.html
https://rdrr.io/cran/dartR/man/gl.amova.html

```{r}
Erigenia_amova<-gl.amova(new_Erigenia_gl)
```

```{r}
Erigenia_amova
```
	Analysis of Molecular Variance

Call: amova(formula = dist ~ pop.names, nperm = perm)

               SSD        MSD  df
pop.names 7.878932 1.12556178   7
Error     1.338694 0.01216994 110
Total     9.217626 0.07878313 117

Variance components:
            sigma2 P.value
pop.names 0.075867       0
Error     0.012170        

Phi-statistics:
pop.names.in.GLOBAL 
          0.8617635 

Variance coefficients:
       a 
14.67554 

Idk what this mean, will have to look into output

```{r}
plot(Erigenia_amova)
```

##poppr
```{r assigning strata}
Erigenia_strata<- read.table("AUG_erigenia.strata.strata_noMD_noYF2", sep= "\t", header= TRUE)
Erigenia_strata
```

```{r}

strata(new_Erigenia_gl) <- Erigenia_strata
new_Erigenia_gl$strata
```

```{r}
poppr_Erigenia_amova<- poppr.amova(new_Erigenia_gl, hier= ~LOCATION)
```
```{r}
poppr_Erigenia_amova
```
ade4::amova(samples = xtab, distances = xdist, structures = xstruct)

$results
                                 Df    Sum Sq    Mean Sq
Between LOCATION                  7 283752.36 40536.0516
Between samples Within LOCATION 110 204550.82  1859.5529
Within samples                  118  47402.94   401.7198
Total                           235 535706.12  2279.6005

$componentsofcovariance
                                                Sigma         %
Variations  Between LOCATION                1317.7194  53.82058
Variations  Between samples Within LOCATION  728.9165  29.77168
Variations  Within samples                   401.7198  16.40774
Total variations                            2448.3557 100.00000

$statphi
                           Phi
Phi-samples-total    0.8359226
Phi-samples-LOCATION 0.6446958
Phi-LOCATION-total   0.5382058

###East West Comparison
```{r}
poppr_Erigenia_amova_EW<- poppr.amova(new_Erigenia_gl, hier= ~REGION)
```
```{r}
poppr_Erigenia_amova_EW
```

$call
ade4::amova(samples = xtab, distances = xdist, structures = xstruct)

$results
                               Df    Sum Sq     Mean Sq
Between REGION                  1 171200.77 171200.7694
Between samples Within REGION 116 317102.41   2733.6415
Within samples                118  47402.94    401.7198
Total                         235 535706.12   2279.6005

$componentsofcovariance
                                              Sigma         %
Variations  Between REGION                1541.0171  49.57115
Variations  Between samples Within REGION 1165.9608  37.50641
Variations  Within samples                 401.7198  12.92245
Total variations                          3108.6978 100.00000

$statphi
                         Phi
Phi-samples-total  0.8707755
Phi-samples-REGION 0.7437489
Phi-REGION-total   0.4957115
