---
title: "Erigenia sNMF"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#LEA sNMF
http://membres-timc.imag.fr/Olivier.Francois/tutoRstructure.pdf
##loading the data and finding clusters
set working directory

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("LEA")
```
```{r}
library(LEA)
library(radiator)
```

put .geno from ipyrad into github folder locally, explore K's, this may take a while.
```{r sNMF pops}
erigenia_snmf = snmf("erigeniaC_noMD.geno", K = 1:8, CPU = 4, entropy = TRUE, project = "new", iterations = 1000, repetitions = 10)
```
project is saved into :
 erigeniaC_noMD.snmfProject 
To load the project, use:
 project = load.snmfProject("erigeniaC_noMD.snmfProject")
To remove the project, use:
 remove.snmfProject("erigeniaC_noMD.snmfProject")

```{r}
project = load.snmfProject("erigeniaC_noMD.snmfProject")
```

```{r sNMF pops}
plot(erigenia_snmf, col = "blue4", cex = 1.4, pch = 19)
```


```{r making structure like plot}
best2 = which.min(cross.entropy(erigenia_snmf, K = 2))
my.colors <- c("tomato", "lightblue")
barchart(erigenia_snmf, K = 2, run = best2,
border = NA, space = 0,
col = my.colors,
xlab = "Individuals",
ylab = "Ancestry proportions",
main = "Ancestry matrix") ->bp1
axis(1, at = 1:length(bp1$order),
labels = bp1$order, las=1,
cex.axis = .3)
```
```{r making structure like plot}
best3 = which.min(cross.entropy(erigenia_snmf, K = 3))
my.colors <- c("tomato", "lightblue", "gold")
barchart(erigenia_snmf, K = 3, run = best3,
border = NA, space = 0,
col = my.colors,
xlab = "Individuals",
ylab = "Ancestry proportions",
main = "Ancestry matrix") ->bp3

axis(1, at = 1:length(bp3$order),
labels = bp3$order, las=1,
cex.axis = .3)
```
```{r making structure like plot}
best5 = which.min(cross.entropy(erigenia_snmf, K = 5))
my.colors <- c("tomato", "lightblue",
"olivedrab", "gold", "cyan")
barchart(erigenia_snmf, K = 5, run = best5,
border = NA, space = 0,
col = my.colors,
xlab = "Individuals",
ylab = "Ancestry proportions",
main = "Ancestry matrix") ->bp5
axis(1, at = 1:length(bp5$order),
labels = bp5$order, las=1,
cex.axis = .3)
```

not sure what this is, but may be good:
```{r p values}
# Population differentiation tests
p = snmf.pvalues(erigenia_snmf,
entropy = TRUE,
ploidy = 2,
K = 2)
pvalues = p$pvalues
par(mfrow = c(2,1))
hist(pvalues, col = "orange")
plot(-log10(pvalues), pch = 19, col = "blue", cex = .7)
```

lfmm quasi gwas thing
```{r adjusted p}
# compute adjusted p-values
p = lfmm.pvalues(erigenia_snmf, K = 5)
pvalues = p$pvalues
# GWAS significance test
par(mfrow = c(2,1))
hist(pvalues, col = "lightblue")
plot(-log10(pvalues), pch = 19, col = "blue", cex = .7)
```

